\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage[english]{babel}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small#4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}} 
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Eduard Chervonenko} \\ \vspace{1pt}
    \href{mailto:ed.chervonenko@gmail.com}{\underline{ed.chervonenko@gmail.com}} $|$ 
    \href{https://t.me/ra1n_xd}{\underline{t.me/ra1n\_xd}} $|$
    \href{https://www.linkedin.com/in/chervonenko-ed}{\underline{linkedin.com/in/chervonenko-ed}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
Fullstack developer with over 3 years of experience building web applications using React, TypeScript, Next.js, and NestJS. Some experience in team leadership, CI/CD setup, and DevOps processes. Passionate about continuous learning and adopting best practices.
%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
    {Frontend Developer}{Feb. 2024 -- Present}
    {Txix}{Remote}
    \resumeItemListStart
        \resumeItem{Refactored legacy projects (migrated from class components and Redux), introduced ESLint and Prettier, improving codebase maintainability, standardizing code style across the team, and boosting performance of updated project versions.}
        \resumeItem{Developed the frontend for a multi-channel communication service (Email, SMS, Push, social networks, messengers), providing the client with a unified interface for managing campaigns across all channels.}
        \resumeItem{Built the frontend for a meeting and electronic voting management service, replacing paper-based workflows and accelerating the decision-making process for the client.}
        \resumeItem{Contributed to the development of an internal UI Kit, unifying the visual style and reducing new interface development time through reusable components.}
    \resumeItemListEnd

\resumeSubheading
    {Fullstack Developer}{Jan. 2021 -- Jul. 2021}
    {SG-Group}{Blagoveshchensk, Russia}
    \resumeItemListStart
        \resumeItem{Built fullstack websites and admin panels from scratch for local businesses (pharmacies, stores, etc.), addressing the region's digitalization needs in the absence of major retail chains.}
        \resumeItem{Integrated third-party services via API on demand, extending products' functionality.}
        \resumeItem{Mentored new developers and introduced Git and Scrum to the company, reducing onboarding time and eliminating code loss.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading
    {Team Lead / Fullstack Developer}{Dec. 2025 -- Present}
    {ManipulA}{Remote}
    \resumeItemListStart
        \resumeItem{Assembled a development team and established processes (task allocation, code review), enabling the MVP of a Telegram bot for a massage salon to launch within one week.}
        \resumeItem{Designed the architecture, set up CI/CD with Telegram notifications, Docker containerization, and log monitoring, reducing release times and accelerating error tracking and resolution.}
        \resumeItem{Implemented Conventional Commits, Semantic Versioning, and wrote comprehensive project documentation, ensuring a transparent change history and faster team workflow.}
    \resumeItemListEnd

\resumeSubheading
    {Mentor / Fullstack Developer}{Jun. 2024 -- Present}
    {6Seniors}{Remote}
    \resumeItemListStart
        \resumeItem{Mentored entry-level developers from zero experience to junior/middle level, created a project knowledge base covering learning processes.}
        \resumeItem{Developed a student attendance monitoring dashboard, giving mentors a visual tool for tracking progress.}
        \resumeItem{Improved the backend and refactored the platform codebase, enhancing stability, visual design, and UX.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
        {Belgorod State University}{Belgorod, Russia}
        {Bachelor's in Computer Science and Information Technology (Honors)}{2020 -- 2024}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} JavaScript, TypeScript, Python, PHP, Go \\
     \textbf{Frontend:} React, Next.js, Vue.js, Redux/RTK, Zustand, SCSS, Ant Design, MUI \\
     \textbf{Backend:} NestJS, FastAPI, Node.js, REST API, GraphQL \\
     \textbf{Databases:} PostgreSQL, MySQL, MongoDB \\
     \textbf{DevOps:} Docker, GitLab CI/CD, Linux, VPS/VDS \\
     \textbf{Tools:} Git, ESLint, Prettier, Vite, Webpack, Figma
    }}
\end{itemize}

\end{document}